Hedonic House Prisce Model King County

### 2023-11-20 Msb205.qmd
:D

```{r}
#| label: setup
#| message: false
library(sf)
library(units)
library(Jmisc)
library(tidyverse)
library(lubridate)
library(sp)
library(spdep)
library(spatialreg)
library(spData)
library(huxtable)
library(knitr)
library(foreign)
library(spdep)
```

@@

```{r Oppgave 1}
kc_house_data <- read.csv("Msb205/Data/kc_house_data.csv")

@@

@@

```{r}
hedon1 %>% 
    linearHypothesis(c("year_month2014-06=0", "year_month2014-07=0",
                       "year_month2014-08=0", "year_month2014-09=0",
                       "year_month2014-10=0", "year_month2014-11=0",
                       "year_month2014-12=0", "year_month2015-01=0",
                       "year_month2015-02=0", "year_month2015-03=0",
                       "year_month2015-04=0", "year_month2015-05=0"),
                     white_adjust = hc3)
```

```{r}
hedon2 %>% 
    linearHypothesis(c("year_month2014-06=0", "year_month2014-07=0",
                       "year_month2014-08=0", "year_month2014-09=0",
                       "year_month2014-10=0", "year_month2014-11=0",
                       "year_month2014-12=0", "year_month2015-01=0",
                       "year_month2015-02=0", "year_month2015-03=0",
                       "year_month2015-04=0", "year_month2015-05=0"),
                     white_adjust = hc4)
```

```{r}
hedon3 %>% 
    linearHypothesis(c("year_month2014-06=0", "year_month2014-07=0",
                       "year_month2014-08=0", "year_month2014-09=0",
                       "year_month2014-10=0", "year_month2014-11=0",
                       "year_month2014-12=0", "year_month2015-01=0",
                       "year_month2015-02=0", "year_month2015-03=0",
                       "year_month2015-04=0", "year_month2015-05=0"),
                     white_adjust = hc1)
```

@@

>>>>

```{r}
#| label: setup
#| message: false
library(sf)
library(units)
library(Jmisc)
library(tidyverse)
library(lubridate)
library(sp)
library(spdep)
library(spatialreg)
library(spData)
library(huxtable)
library(knitr)
library(foreign)
library(spdep)
library(car)
```

@@

```{r Oppgave 1}
kc_house_data <- read.csv("Data/kc_house_data.csv")

@@

**3 narmeste naboer**

![](Data/img/Skjermbilde 2023-11-20 094933.png)

![](Data/img/Skjermbilde 2023-11-20 095031.png)

![](Data/img/Skjermbilde 2023-11-20 095117.png)

![]()

![](Data/img/Skjermbilde 2023-11-20 095434.png)

**10 nærmeste naboer**

![](Data/img/Skjermbilde 2023-11-20 100029.png)

![](Data/img/Skjermbilde 2023-11-20 100053.png)

![](Data/img/Skjermbilde 2023-11-20 100120.png)

![](Data/img/Skjermbilde 2023-11-20 100137.png)

![](Data/img/Skjermbilde 2023-11-20 100151.png)

![](Data/img/Skjermbilde 2023-11-20 100208.png)

![](Data/img/Skjermbilde 2023-11-20 100232.png)

@@

```{r}
#| eval: false
hedon1 %>% 
    linearHypothesis(c("year_month2014-06=0", "year_month2014-07=0",
                       "year_month2014-08=0", "year_month2014-09=0",
                       "year_month2014-10=0", "year_month2014-11=0",
                       "year_month2014-12=0", "year_month2015-01=0",
                       "year_month2015-02=0", "year_month2015-03=0",
                       "year_month2015-04=0", "year_month2015-05=0"),
                     white_adjust = hc3)
```

```{r}
#| eval: false
hedon2 %>% 
    linearHypothesis(c("year_month2014-06=0", "year_month2014-07=0",
                       "year_month2014-08=0", "year_month2014-09=0",
                       "year_month2014-10=0", "year_month2014-11=0",
                       "year_month2014-12=0", "year_month2015-01=0",
                       "year_month2015-02=0", "year_month2015-03=0",
                       "year_month2015-04=0", "year_month2015-05=0"),
                     white_adjust = hc4)
```

```{r}
#| eval: false
hedon3 %>% 
    linearHypothesis(c("year_month2014-06=0", "year_month2014-07=0",
                       "year_month2014-08=0", "year_month2014-09=0",
                       "year_month2014-10=0", "year_month2014-11=0",
                       "year_month2014-12=0", "year_month2015-01=0",
                       "year_month2015-02=0", "year_month2015-03=0",
                       "year_month2015-04=0", "year_month2015-05=0"),
                     white_adjust = hc1)
```

@@

```{r}
KC_husdata <- KC_husdata %>% 
  filter(!is.na(EHD_percen))
```

```{r}
mod2 <- "log(price) ~ log(sqft_living) + log(sqft_lot) + log(yr_built) + log(high) + log(I(andel_svart_alene + 1)) + waterfront + view"
```

```{r}
lm_mod2 <- lm(mod2, data = KC_husdata)
```

```{r}
summary(lm_mod2)
```
